Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-08 docs/proposal/proposal.tex
minor corrections
more tex

\date{}
\maketitle{}

\section{Abbreviations}
\begin{itemize}[label={--}, left=0.25cm] % Adjust label and left indent as desired
    \item FPGA: Field Programmable Gate Array
    \item VLSI: Very Large Scale Integration
    \item EDA: Electronic Design Automation
    \item VHSIC: Very High Speed Integrated Circuits
    \item HDL: Hardware Description Language
    \item VHDL: VHSIC HDL
    \item HLS: High Level Synthesis
    \item PL-PS: Programmable Logic - Processing System
\end{itemize}

@@

    \item \textbf{EDA}: Electronic Design Automation
    \begin{itemize}[label={--}, left=0.25cm]
        \item Proprietary software for FPGA and VLSI development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item Xilinx - Vivado (Design + Simulation) + Vitis (HLS + PL-PS codesign)
            \item Altera - Quartus (Design) + ModelSim (Simulation)
            \item Synopsis (VLSI)
            \item Cadence (VLSI)
        \end{itemize}
        \item Open source software for FPGA development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item VTR: a PNR tool popular amongst researchers who study placement techniques
            \item OSS-CAD: a full-flow software suite that includes ABC synthesis, Yosys synthesis, Yosys nextpnr.
            \item AMF-Placer (Analytical Placer)
            \item DREAMPlace (VLSI) + DREAMPlaceFPGA
            \item RapidLayout (Hard Block Placer)
            \item RapidStream (Systolic Array Placer)
            \item RapidWright: Semi-open source API that provides backend access to Xilinx Vivado EDA using design checkpoints.

        \end{itemize}
    \end{itemize}

    \item \textbf{Synthesis}
    \begin{itemize}[label={--}, left=0.25cm]
        \item 
        \item 
        \item 
        \item 
    \end{itemize}
\end{itemize}

>>>>

\date{}
\maketitle

\section{Abbreviations}
\begin{itemize}[label={--}, left=0.25cm] % Adjust label and left indent as desired
    \item FPGA: Field Programmable Gate Array
    \item VLSI: Very Large Scale Integration
    \item EDA: Electronic Design Automation
    \item VHSIC: Very High Speed Integrated Circuits
    \item HDL: Hardware Description Language
    \item VHDL: VHSIC HDL
    \item HLS: High Level Synthesis
    \item PL-PS: Programmable Logic - Processing System
    \item EDIF: Electronic Design Interchange Format
\end{itemize}

@@

    \item \textbf{EDA}: Electronic Design Automation
    \begin{itemize}[label={--}, left=0.25cm]
        \item Proprietary software for FPGA and VLSI development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item Xilinx - Vivado (Design + Simulation) + Vitis (HLS + PL-PS codesign)
            \item Altera - Quartus (Design) + ModelSim (Simulation)
            \item Synopsis (VLSI)
            \item Cadence (VLSI)
        \end{itemize}
        \item Open source software for FPGA development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item VTR: a PNR tool popular amongst researchers who study placement techniques
            \item OSS-CAD: a full-flow software suite that includes ABC synthesis, Yosys synthesis, Yosys nextpnr.
            \item AMF-Placer (Analytical Placer)
            \item DREAMPlace (VLSI) + DREAMPlaceFPGA
            \item RapidLayout (Hard Block Placer for Systolic Arrays)
            \item RapidStream (HLS Placer)
            \item RapidWright: Semi-open source API that provides backend access to Xilinx Vivado EDA using design checkpoints.
        \end{itemize}
    \end{itemize}

    \item \textbf{Synthesis}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes a design written in a high-level HDL like VHDL or Verilog and "synthesizes" a \textbf{logical netlist} out of it. This logical netlist is usually generated as an EDIF, JSON, or a low-level Verilog file. This netlist describes the necessary basic elements of logic (BELs) and the wired connections between them that are necessary to implement the design.
    \end{itemize}

    \item \textbf{Placement}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{logical netlist} and produces a \textbf{physical netlist}.
    \end{itemize}

    \item \textbf{Routing}
    \begin{itemize}[label={--}, left=0.25cm]
        \item Takes the \textbf{physical netlist} and maps the connections between BELs onto physical switchboxes.
    \end{itemize}

\end{itemize}

This is a citation for AMFPlacer. \cite{AMFPlacer}

\bibliographystyle{ieeetr}
\bibliography{references}
